---
title: "Download and work with data from OpenStreetMap"
author: "Jan-Philipp Kolb"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,echo=F}
ca <- T
Val_eval=F
```



## Introduction

The `geoosmdata2` package is designed to download and process data from OpenStreetMap. 
The [Overpass](http://wiki.openstreetmap.org/wiki/Overpass_API)-API is used to get data out of OpenStreetMap.The package is a wrapper for this API.

Many functions are available which will be desrcibed in the following. The first section is about geocoding with geosmadata2 package which uses the [Nominatim](http://wiki.openstreetmap.org/wiki/Nominatim) functionality. 

```{r,cache=ca,eval=Val_eval}
library(geosmdata2)
```

## Geocoding with nominatim

```{r,cache=ca,eval=Val_eval}
gc <- geocode_osm("rue Saint Vincent Paris",output="all")
```

## Get information on points of interest (POI)

```{r,cache=ca,eval=Val_eval}
cafes <- get_osm_nodes("cafe",place="Concord")

cafes_cc <- extract_info_op(OSM.Data=cafes,value="cafe")
```

Get information about Hostels in a city:

```{r hostels,cache=T}
library(geosmdata2)
place <- "Madrid"
object <- "hostel"
obj <- get_osm_nodes(object,place)
op <- extract_info_op(obj,object)
```



The `ggmap` function from package [ggmap](https://cran.r-project.org/web/packages/ggmap/index.html) can be used to download a background map. 


```{r stamenMap,message=F,cache=T}
place_map12stamen <- qmap(place, zoom = 12,
                          maptype="toner-lite",
                          source="stamen")
```


```{r}
place_map12stamen + geom_point(aes(x = lon, y = lat),
                       data = op,size=3,col="red") 
```


```{r,cache=ca,eval=Val_eval}
library(ggmap)
Concord_map <- get_googlemap("Concord")
ggmap(Concord_map)+ geom_point(aes(x = lon, y = lat),
data = cafes_cc)
```



## Area

```{r,cache=ca,eval=Val_eval}

Rom_pedestrian <- get_osm_area(object2="pedestrian",
                               place="Rom")
info_pedestrian <- extract_info_op(OSM.Data=Rom_pedestrian,
                                    value="pedestrian")

```

## Get information about bicycle routes

```{r,cache=ca,eval=Val_eval}
MA_cycle1 <- get_osm_ways(object2="cycleway",place="Mannheim")
MA_bike_routes <- extract_position_op(MA_cycle1,"cycleway")
```



## Relation

> "A relation is one of the core data elements that consists of one or more tags and also an ordered list of one or more nodes, ways and/or relations as members which is used to define logical or geographic relationships between other elements. A member of a relation can optionally have a role which describe the part that a particular feature plays within a relation. "
([via](http://wiki.openstreetmap.org/wiki/Relation))

```{r,eval=F,cache=ca,eval=Val_eval}
MA_bike_routes <- get_osm_relation("bicycle","Mannheim")

info_bike_routes <- extract_info_op(OSM.Data=MA_bike_routes,
                                    value="bicycle")
```

