---
title: "Download and work with data from OpenStreetMap"
author: "Jan-Philipp Kolb"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


## Introduction

The `geoosmdata2` package is designed for the download and work with data from OpenStreetMap. 

[Overpass-turbo](https://www.mapbox.com/guides/overpass-turbo/) is an alternative, but no API. 


```{r}
library(geosmdata2)
```

## Geocoding with nominatim

```{r}
gc <- geocode_osm("rue Saint Vincent Paris",output="all")
```


## Area

```{r}

Rom_pedestrian <- get_osm_area(object2="pedestrian",
                               place="Rom")
info_pedestrian <- extract_info_op(OSM.Data=Rom_pedestrian,
                                    value="pedestrian")

```

## Get information about bicycle routes

```{r}
MA_cycle1 <- get_osm_ways(object2="cycleway",place="Mannheim")
```



## Relation

> "A relation is one of the core data elements that consists of one or more tags and also an ordered list of one or more nodes, ways and/or relations as members which is used to define logical or geographic relationships between other elements. A member of a relation can optionally have a role which describe the part that a particular feature plays within a relation. "
([via](http://wiki.openstreetmap.org/wiki/Relation))

```{r,eval=F}
MA_bike_routes <- get_osm_relation("bicycle","Mannheim")

info_bike_routes <- extract_info_op(OSM.Data=MA_bike_routes,
                                    value="bicycle")
```

