---
title: "Packete Choroplethr und DT"
author: "Jan-Philipp Kolb"
date: "Fri Sep 04 14:08:29 2015"
output: ioslides_presentation
---

```{r,echo=F}
library(knitr)
library(DT)
internet <- F
Nint <- !internet
```

## Introduction

[`choroplethr`](https://cran.r-project.org/web/packages/choroplethr/index.html) - Simplify the Creation of Choropleth Maps in R

Package by [Ari Lamstein](http://www.arilamstein.com/)

[`WDI`](https://cran.r-project.org/web/packages/WDI/index.html)
- World Development Indicators (World Bank)

The following relies heavily on the [vignette](https://cran.r-project.org/web/packages/choroplethr/index.html) of the `choroplethr`-package

## What is a choropleth map

A choropleth is a map which

- shows geographic boundaries.
- colors those regions based on some metric.

Choropleths are useful for visualizing data where geographic boundaries are a natural unit of aggregation. 

## Population estimates for US States

```{r,warning=F,message=F,echo=F}
library("choroplethr")
data(df_pop_state)
```

`df_pop_state` is a dataset which is included in the package `choroplethr`, containing population estimates for US States in 2012.

```{r,echo=F,eval=internet}
library("choroplethrMaps")
datatable(df_pop_state,options = list(pageLength = 5))
```

```{r,echo=F,eval=Nint}
kable(df_pop_state[1:10,])
```

## `choroplethr` - Hello World

For example, here is a [choropleth](http://mirrors.softliste.de/cran/web/packages/choroplethr/vignettes/a-introduction.html) that shows 2012 US State Population Estimates:

We get a choropleth map with only one argument:

```{r}
state_choropleth(df_pop_state)
```


But we can also create a title and name the legend:

```{r}
state_choropleth(df_pop_state, title="2012 US State Population Estimates", legend="Population")
```

## Show only three states

[US State Chropleths](http://mirrors.softliste.de/cran/web/packages/choroplethr/vignettes/b-state-choropleth.html)

```{r}
state_choropleth(df_pop_state,
                 title      = "2012 Population Estimates",
                 legend     = "Population",
                 num_colors = 1,
                 zoom       = c("california", "washington", "oregon"))
```


## US County Chropleths

[Choropleth of US Counties](http://mirrors.softliste.de/cran/web/packages/choroplethr/vignettes/c-county-choropleth.html)

```{r,eval=F}
?df_pop_county

?county_choropleth
```


```{r}
data(df_pop_county)

county_choropleth(df_pop_county)
```


## [Country Choropleths ](http://mirrors.softliste.de/cran/web/packages/choroplethr/vignettes/d-country-choropleth.html)

```{r}
data(df_pop_country)

country_choropleth(df_pop_country,
                 title      = "2012 Population Estimates",
                 legend     = "Population",
                 num_colors = 1,
                 zoom       = c("united states of america", "mexico", "canada"))
```



## World Bank data

```{r,cache=T,warning=F,message=F}
library(choroplethr)
library(WDI) 

choroplethr_wdi(code="SP.POP.TOTL", year=2012, title="2012 Population", num_colors=1)
```

## [Life Expectancy](http://mirrors.softliste.de/cran/web/packages/choroplethr/vignettes/f-world-bank-data.html)

```{r,warning=F,message=F}
library(WDI) 
choroplethr_wdi(code="SP.DYN.LE00.IN", year=2012, title="2012 Life Expectancy")
```


## Animated

```{r,cache=T}
data(df_president_ts)
```

With the questionmark we get help

```{r,eval=F}
?df_president_ts
```


## The datatable

```{r,cache=F,echo=F,warning=F,eval=internet}
datatable(df_president_ts, options = list(pageLength = 5))
```

- [datatable](http://www.htmlwidgets.org/showcase_datatables.html)

## Resources / Links

- [Intro - What is a choropleth](https://cran.r-project.org/web/packages/choroplethr/vignettes/a-introduction.html)

- [Description](http://radar.oreilly.com/2014/01/new-choropleth-package-in-r.html) on the usage of the `choroplethr` package

- Plot the [US states](https://cran.r-project.org/web/packages/choroplethr/vignettes/b-state-choropleth.html) with `choroplethr`

- [Mapping World Bank Data](https://cran.r-project.org/web/packages/choroplethr/vignettes/f-world-bank-data.html) with `choroplethr`

- [Revolutions-blog](http://blog.revolutionanalytics.com/2014/01/easy-data-maps-with-r-the-choroplethr-package-.html) on the `choroplethr` package

- [trulia](http://www.trulia.com/tech/2014/01/15/the-choroplethr-package-for-r/)-blog on the `choroplethr` package

- [Presentation Ari Lamstein](http://www.r-bloggers.com/slides-for-my-upcoming-talk-mapping-census-data-in-r/) on the `choroplethr` package
