---
title: "maps package"
author: "Jan-Philipp Kolb"
date: "Fri Sep 18 14:22:39 2015"
output: slidy_presentation
---

```{r,echo=F,warning=F}
library(knitr)
Ex=T
```


## Polische Karte:

- Eine politische Karte zeigt keine topographischen Informationen.

- Hauptsächlich sollen adminstrative Grenzen dargestellt werden.

- Teilweise werden auch Städte mit eingezeichnet

- Ein typisches Beispiel ist eine Karte der US-Staaten

## Political Map

```{r,echo=F,message=F,warning=F,eval=F}
library(maps)
library(magrittr)
library(leaflet)
mapStates = map("state", fill = TRUE, plot = FALSE)
leaflet(data = mapStates) %>% addTiles() %>%
  addPolygons(fillColor = topo.colors(10, alpha = NULL), stroke = FALSE)
```

```{r,echo=F,message=F,warning=F}
library(maps)
map("state",fill=T,col=1:10)
```



## Das R-Paket maps

```{r,message=F}
library(maps)
```

Wie man Hilfe bekommt:

```{r,eval=F}
?map
```



## Hallo Welt

```{r}
map()
```


## Ein erstes Argument

Der gleiche Befehl mit einem Argument:

```{r}
map("usa")
```

## Eine Frankreichkarte

```{r}
map("france")
```

## Politische Karte - Italien
Get the borders in blue color:
```{r}
library ( maps )
map ("italy", col = "blue")
```

## Choropleths - package maps

If we want the areas in blue:
```{r}
map ("italy",fill =T, col = "blue")
```

## More colors

Create a vector:

```{r}
colors <- c("blue","red","yellow")
```

and use the vector to specify the color

```{r}
map ("italy",fill =T, col = colors)
```

## Excursus: more colors!
You can also use the [rgb](https://stat.ethz.ch/R-manual/R-devel/library/grDevices/html/rgb.html) command to create your own colors:

```{r}
map("italy",fill=T, col = rgb(0,1,0))
```

## Try also

```{r,eval=F}
map("italy",fill=T, col = rgb(1,0,0))
map("italy",fill=T, col = rgb(1,1,1))
map("italy",fill=T, col = rgb(1,0.5,0.4))
```

## Choropleths - package maps
If you want to know, which region is at which place:

```{r}
italy <- map("italy", plot = F)
head(italy$names)
```

## Maps with only one argument

```{r,eval=F}
map("county")
```


```{r,echo=F}
Argument <- c("county","france","italy","nz","state","usa","world")
What <- c("US Counties","France","Italy","New Zealand","US States","USA","Countries of the world")

kable(data.frame(Argument,What))
```


## A map for Germany

```{r}
library(maps)
map("world", "Germany")
```

## Package maps - two countries


```{r}
map("world", c("Germany","Poland"))
```


## Two countries with color

```{r}
map("world", c("Germany","Austria"),fill=T,
col=c("red","green"))
```



## Package maps - additional features

```{r}
map("world", "China")
map.scale()
```

## Package maps - additional features

Like `map`, but labels the regions:

```{r}
map.text("county", "penn")
```

Pennsylvania counties

## R-package maps - World cities

`data` loads specified data sets, or lists the available data sets.

```{r}
data(world.cities)
```

`head` - Return the First Part of an Object

```{r,eval=F}
head(world.cities)
```

## Overview of world cities data

```{r,echo=F}
kable(head(world.cities))
```

## Map the cities of the world


```{r}
map()
map.cities(world.cities)
```

## Cities of France

```{r}
data(world.cities)
map("france")
map.cities(world.cities)
```

## Only cities of France

```{r}
FrenchCity <- world.cities$country.etc=="France"
FCit <- world.cities[FrenchCity,]
```

```{r,echo=F}
kable(head(FCit,n=4))
```


## Only cities of France

Now it is possible to map only the french cities:

```{r}
map("france")
map.cities(FCit,col="blue",pch=20)
```

`pch` - plotting character, i.e., symbol to use.


## Different sizes - different colors 

```{r}
FCit_Bc<-FCit[FCit$pop>50000,]
map("france")
map.cities(FCit,col="blue",pch=20)
map.cities(FCit_Bc,col="red",pch=20)
```

## Thematic maps with R-package maps

Data basis - CIA World DataBank II

The [CIA World DataBank](http://www.evl.uic.edu/pape/data/WDB/) is a collection of world map data, consisting of vector descriptions of land outlines, rivers, / political boundaries. It was created by U.S. government in the 1980s.

## Example: US Unemployment 

- [More](http://bcb.dfci.harvard.edu/~aedin/courses/R/CDC/maps.html) about the usage of package maps


Get the data:
```{r}
library(maps)
data(unemp)
data(county.fips)
```

## Color gradients 

```{r,warning=F}
library(colorRamps)
colors <- blue2red(6)
barplot(1:6,col=colors)
```

## Example: US Unemployment - color coding

```{r}
unemp$colorSteps <- cut(unemp$unemp, 
          c(0, 2, 4, 6, 8,10, 100))
colorsmatch <- unemp$colorSteps[match(county.fips$fips, 
          unemp$fips)]
```


## Example: US Unemployment 

```{r}
map("county", col = colors[colorsmatch], 
    fill = TRUE)
```

## Further links and resources

- [Using R — Working with Geospatial Data](http://mazamascience.com/WorkingWithData/?p=1277)

- Robin Lovelace, James Cheshire - [Introduction to visualising spatial data in R](https://cran.r-project.org/doc/contrib/intro-spatial-rl.pdf)

- [Maps in R: Introduction - Drawing the map of Europe](http://www.milanor.net/blog/?p=534)