---
title: "Package spdep"
author: "Jan-Philipp Kolb"
date: "08 April 2016"
output: ioslides_presentation
---

## Das erste Gesetz der Geographie (TFLG)


> "All things are related, but nearby things are more related than distant things"
[Tobler, 1970]


## Eine Karte von Afrika

```{r,warning=F,message=F}
library(maptools)
data(wrld_simpl)
Africa <- wrld_simpl[wrld_simpl@data$REGION==2,]
plot(Africa)
```


## Get the center of a polygon

```{r,warning=F,message=F}
library(sp)
Af <- coordinates(Africa)
plot(Africa)
points(x=Af[1,1],y=Af[1,2],col="red",pch=20)
```

## Find the nearest neighbours

```{r,warning=F,message=F}
library(spdep)
Af_nb <- tri2nb(Af)
```

The neighbours for the first country:

```{r,warning=F,message=F}
Af_nb[1]
```

## Find the nearest neighbours

```{r,warning=F,message=F}
plot(Africa)
plot(Africa[1,],col="red",add=T)
plot(Africa[Af_nb[1][[1]],],col="orange",add=T)
```

## Find the nearest 10 neighbours

```{r,warning=F,message=F}
IDs <- row.names(as(Africa, "data.frame"))
Af10_nb <- knn2nb(knearneigh(Af, k = 10), row.names = IDs)
plot(Africa)
plot(Africa[1,],col="red",add=T)
plot(Africa[Af10_nb[1][[1]],],col="orange",add=T)
```

## Compute the distance

```{r,warning=F,message=F}
Af <- coordinates(Africa) # get centroid
library(raster)
pointDistance(Af[1:4,], lonlat=TRUE) # compute distance
```

## Compute/plot a distance matrix

```{r Africa Distance,warning=F,message=F}
Dist_Af <- pointDistance(Af, lonlat=TRUE)
Af_color <- Dist_Af[,1]
Af_color <- Af_color/max(Af_color)
Af_color <- rgb(Af_color,0,0)
plot(Africa,col=Af_color)
```


## Links

- [Raster, CMSAF and solaR](https://procomun.wordpress.com/2011/06/17/raster-cmsaf-and-solar/)

- [Getting rasters into shape from R](https://johnbaumgartner.wordpress.com/2012/07/26/getting-rasters-into-shape-from-r/)