---
title: "Hello world"
author: "Jan-Philipp Kolb"
date: "21. April 2015"
output: html_document
---

## The first library

- R is a modular programmin language
- For many tasks it is necessary to load packages

```{r,message=F}
  # install the library
# install.packages("maps")

  # load the library
library(maps)
```

## Hello world

```{r}
map("world")
```


## A map of the USA

- with the argument col, it is possible to specify the border color 

```{r}
map('usa',col="blue")
```


## A map of France

```{r}
map("france",fill=T,col="green")
```


## A map of Italy

- get more than one color

```{r}
map("italy",fill=T, col = 1:10)
```

## A map of US-states

```{r}
map("state")
```


## Maps of other countries

- For most of the countries you have to specify two arguments:

```{r}
map("world", "Germany")
```


## More than one country in a map

```{r}
map("world", c("Germany","Poland"))
```


## More than one country in a map with colors

```{r}
map("world", c("Germany","Austria"),fill=T,col=c("red","green"))
```

## Map scales

```{r}
map("world", "China")
map.scale()
```

## Maps with labels

```{r}
map.text("world", "Germany")
```

## Cities data set

```{r}
data(us.cities)
```



```{r,results='asis',echo=F}
library(knitr)
kable(head(us.cities))
```


## Map German cities

```{r}
map("world", "Germany")
map.cities(country = "Germany")
```

## Map only capital

```{r}
map("world", "Germany")
map.cities(country = "Germany",capitals=1)
```

## Data set world cities

```{r}
data(world.cities)
```


```{r,results='asis',echo=F}
kable(head(world.cities))
```

## Change type of symbol

```{r}
map("world", "Germany")
map.cities(country = "Germany",pch=20,col="red")
```


