---
title: "maps package"
author: "Jan-Philipp Kolb"
date: "17. Juli 2015"
output: ioslides_presentation
---

```{r,echo=F}
library(knitr)
```



## The maps package

```{r,message=F}
library(maps)
?map
```

## A first map

```{r}
map()
```


## A first argument

The same command with an argument:

```{r}
map("usa")
```

## A map of france

```{r}
map("france")
```

## Choropleths - package maps
Get the borders in blue color:
```{r}
library ( maps )
map ("italy", col = "blue")
```

## Choropleths - package maps

If we want the areas in blue:
```{r}
map ("italy",fill =T, col = "blue")
```

## More colors

Create a vector:

```{r}
colors <- c("blue","red","yellow")
```

and use the vector to specify the color

```{r}
map ("italy",fill =T, col = colors)
```

## Excursus: more colors!
You can also use the [rgb](https://stat.ethz.ch/R-manual/R-devel/library/grDevices/html/rgb.html) command to create your own colors:

```{r}
map("italy",fill=T, col = rgb(0,1,0))
```

## Try also

```{r,eval=F}
map("italy",fill=T, col = rgb(1,0,0))
map("italy",fill=T, col = rgb(1,1,1))
map("italy",fill=T, col = rgb(1,0.5,0.4))
```

## Choropleths - package maps
If you want to know, which region is at which place:

```{r}
italy <- map("italy", plot = F)
head(italy$names)
```

## A map for Germany

```{r}
library(maps)
map("world", "Germany")
```

## Choropleths - package maps - two countries


```{r}
map("world", c("Germany","Poland"))
```


## 2 countries with color

```{r}
map("world", c("Germany","Austria"),fill=T,
col=c("red","green"))
```


## Choropleths - package maps - additional features

```{r}
map("world", "China")
map.scale()
```

## Choropleths - package maps - additional features

Like `map`, but labels the regions:

```{r}
map.text("county", "penn")
```

Pennsylvania counties

## R-package maps - World cities

`data` loads specified data sets, or lists the available data sets.

```{r}
data(world.cities)
```

`head` - Return the First Part of an Object

```{r,eval=F}
head(world.cities)
```

## Overview of world cities data

```{r,echo=F}
kable(head(world.cities))
```

## Map the cities of the world


```{r}
map()
map.cities(world.cities)
```

## Cities of France

```{r}
data(world.cities)
map("france")
map.cities(world.cities)
```

## Only cities of France

```{r}
FrenchCity <- world.cities$country.etc=="France"
FCit <- world.cities[FrenchCity,]
```

```{r,echo=F}
kable(head(FCit,n=4))
```


## Only cities of France

Now it is possible to map only the french cities:

```{r}
map("france")
map.cities(FCit,col="blue",pch=20)
```

`pch` - plotting character, i.e., symbol to use.


## Different sizes - different colors 

```{r}
FCit_Bc<-FCit[FCit$pop>50000,]
map("france")
map.cities(FCit,col="blue",pch=20)
map.cities(FCit_Bc,col="red",pch=20)
```

## Data basis - CIA World DataBank II

The [CIA World DataBank](http://www.evl.uic.edu/pape/data/WDB/) is a collection of world map data, consisting of vector descriptions of land outlines, rivers, / political boundaries. It was created by U.S. government in the 1980s.
