---
title: "sp package"
author: "Jan-Philipp Kolb"
date: "04/22/2015"
output: ioslides_presentation
---



```{r,echo=F}
library(knitr)
ca <- T
```

## The package sp

- classes and methods for spatial data

```{r,message=F,cache=ca,warning=F}
library(sp)
```

## Hello world

- A first example using data from maptools ([ISO2-codes](http://en.wikipedia.org/wiki/ISO_3166-1_alpha-2))


```{r,message=F,cache=ca,warning=F}
library(maptools)
data("wrld_simpl")
ind <- wrld_simpl@data$ISO2%in%c("FR","DE","AT","CH")
my_map <- wrld_simpl[ind,]
plot(my_map)
```


## The data set

```{r,eval=F,cache=ca,warning=F}
head(my_map@data)
```


```{r,echo=F,cache=ca,warning=F}
library(knitr)
kable(my_map@data[1:4,1:5])
```



## First example

```{r,cache=ca,warning=F}
spplot(my_map,"POP2005")
```

## Using `colorRamps`

```{r,message=F,cache=ca,warning=F}
library(colorRamps)
spplot(my_map,"POP2005",col.regions=blue2red(100))
```

## Using `colorRamps`

```{r,cache=ca,warning=F}
spplot(my_map,"POP2005",col.regions=blue2green(100))
```

## Using `colorRamps`

```{r,cache=ca,warning=F}
spplot(my_map,"POP2005",col.regions=green2red(100))
```

## Using `colorRamps`
```{r,cache=ca,warning=F}
spplot(my_map,"POP2005",col.regions=blue2yellow(100))
```

## Using `colorRamps`
```{r,cache=ca,warning=F}
spplot(my_map,"POP2005",col.regions=matlab.like(100))
```

## Using synthetic data

Generating synthetic data (Population 2010)

```{r,cache=ca,warning=F}
my_map$Pop2010 <- my_map$POP2005 + 
runif(length(my_map),-10000,10000)
```


## Colors [matlab](http://de.mathworks.com/products/matlab/) like

```{r,cache=ca,warning=F}
spplot(my_map,c("POP2005","Pop2010"),
       col.regions=matlab.like(100))
```

## More examples 

- [Stamen maps with spplot](https://procomun.wordpress.com/2013/04/24/stamen-maps-with-spplot/)

- [Know India through visualisation](http://justanotherdatablog.blogspot.de/2014/02/know-india-through-visualisations-1.html)

- [Great circles](https://procomun.wordpress.com/2011/05/20/great-circles/)

- [Canadian vote compass](http://blog.revolutionanalytics.com/2011/12/vote-compass-visualizing-canadian-poll-results-with-r.html)

- [More colors in R](http://www.r-bloggers.com/using-the-new-viridis-colormap-in-r-thanks-to-simon-garnier/)
