---
title: "Data sources"
author: "Jan-Philipp Kolb"
date: "24. April 2015"
output: ioslides_presentation
---


## OpenStreetMap

> OpenStreetMap (OSM) is a collaborative project to create a free editable map of the world.

[Wikipedia - OpenStreetMap](https://en.wikipedia.org/wiki/OpenStreetMap)

## Data from Open Street Map

```{r,message=F}
library(osmar)
api <- osmsource_api()
library(ggmap)
```

## Download OSM data 

```{r}
cityC <- geocode("Berlin")
bb <- center_bbox(cityC$lon,cityC$lat,1000, 1000)
uaBerlin <- get_osm(bb, source = api)
```

## TwittR

```{r,eval=F}
library(twitteR)
library(streamR)
```


<http://www.r-bloggers.com/mapping-the-world-with-tweets-including-a-gif-without-cats-and-a-shiny-app/>

## The worldHires data

```{r}
library(mapdata)
data(worldHiresMapEnv)
map('worldHires', col=1:10)
```


## Historic data

[Historic geocoder](http://www.azavea.com/blogs/newsletter/v2i3/azavea-research-historic-geocoder/)


```{r}
library(HistData)
data(Arbuthnot)
```

## Data for the US

```{r,eval=F}
library(UScensus2000)
```

## GDELT data

- [GDELT](http://www.gdeltproject.org/)
- [Kalev Leetaru](http://www.kalevleetaru.com/)
- [Example on usage of GDELT data](http://quantifyingmemory.blogspot.de/2013/04/mapping-gdelt-data-in-r-and-some.html)

```{r,eval=F}
library(GDELTtools)
test.filter <- list(ActionGeo_ADM1Code=c("NI", "US"), ActionGeo_CountryCode="US")
test.results <- GetGDELT(start.date="1979-01-01", end.date="1979-12-31",
                         filter=test.filter)
```


## Package `datasets`

```{r}
library(datasets)
```



## Other data sources

- [Census results - Germany](https://ergebnisse.zensus2011.de/)
- [Census results - Britain](http://www.r-bloggers.com/2011-census-open-atlas-project/) and [boundaries](http://www.ons.gov.uk/ons/guide-method/census/2011/census-data/2011-census-prospectus/new-developments-for-2011-census-results/2011-census-geography/2011-census-geography-prospectus/index.html)
- [Data on airports](http://openflights.org/data.html) and an [example](http://www.milanor.net/blog/?p=594) on the usage in R


## [ADFC/opengeodb](http://www.fa-technik.adfc.de/code/opengeodb/)

Bicycle Coding

```{r}
link <- "http://www.fa-technik.adfc.de/code/opengeodb/DE9.tab"
info <- read.csv(link,sep="\t",header=F)
```


## Further resources

- [OpenGov](http://ropengov.github.io/projects/)

- [metro extracts - City-sized portions of OpenStreetMap](https://mapzen.com/data/metro-extracts/)
