---
title: "Interesting Links"
author: "Jan-Philipp Kolb"
date: "24. April 2015"
output: html_document
---


## Intro R

<http://manuals.bioinformatics.ucr.edu/home/programming-in-r>

[Teaching R](http://www.r-bloggers.com/teaching-a-short-topic-to-beginner-r-users/)

[Data Wrangling etc.](http://stat545-ubc.github.io/)

[youtube on R](http://www.revolutionanalytics.com/what-r)

## Popularity R

On [Usage of R in Germany](http://www.gulli.com/news/23740-programmiersprache-r-in-der-wissenschaft-immer-beliebter-2014-04-24). R in an [article in the New York Times](http://community.oreilly.de/blog/2011/01/18/statistiksoftware-r/)



<http://www.nytimes.com/2009/01/07/technology/business-computing/07program.html?_r=0>

<http://www.r-bloggers.com/top-100-r-packages-for-2013-jan-may/>

<http://www.r-bloggers.com/a-list-of-r-packages-by-popularity/>



## Making maps

- A very [comprehensive tutorial](http://pakillo.github.io/R-GIS-tutorial) was published by [Francisco Rodriguez-Sanchez](https://sites.google.com/site/rodriguezsanchezf/). 

- [Hints](http://giswerk.org/) on the usage of OpenStreetMap data with R

- [Task view for mapping tools](https://github.com/ropensci/maptools)

- [Another Intro on making maps](http://www.molecularecologist.com/2012/09/making-maps-with-r/)

- [More](https://github.com/Robinlovelace/osm-tutorial/blob/master/osm.Rmd)


## Making more maps

[Example 1](http://www.r-bloggers.com/reot-empirical-orthogonal-teleconnections-in-r/)

[Example 2](http://blog.revolutionanalytics.com/2013/08/visualizing-katrinas-strongest-winds-with-r.html)

[Example 3](http://www.r-bloggers.com/here-comes-the-sun/)

[Example 4](http://www.r-bloggers.com/maps-of-solar-radiation/)

[Example 5](http://www.r-bloggers.com/choropleths-made-easy/)

## More Intros - making maps with R

- [part 1](http://procomun.wordpress.com/2012/02/18/maps_with_r_1/)
- [part 3](http://procomun.wordpress.com/2012/02/23/maps_with_r_3/)

## Work with OpenStreetMap data

In general (three osm apis):
<http://www.d-mueller.de/blog/open-streetmap-api-tutorial-umkreissuche/>


<http://www.r-bloggers.com/mapping-the-world-with-tweets-including-a-gif-without-cats-and-a-shiny-app/>

<file:///D:/Dropbox/RForschung/SpatialCourse/Rcode/makingmaps/makingmaps.html>



<http://thematicmapping.org/downloads/world_borders.php>

<http://www.r-bloggers.com/introductory-point-pattern-analysis-of-open-crime-data-in-london/>


<http://www.r-bloggers.com/stop-and-frisk-spatial-analysis-of-racial-discrepancies/>

<http://www.r-bloggers.com/organize-a-walk-around-london-with-r/>


[Visualizing GIS data with R and Open Street Map](http://www.r-bloggers.com/visualizing-gis-data-with-r-and-open-street-map/>)

## Information from OpenStreetMap

<https://mapzen.com/data/metro-extracts/>


## Interactive maps

<http://r-video-tutorial.blogspot.ch/2015/05/exchange-data-between-r-and-google-maps.html>

Google maps:



## Flowing data

Where people run

<http://flowingdata.com/2014/02/05/where-people-run/>

## R conferences

<http://www.r-bloggers.com/some-r-conferences-in-2015/>

get an overview of events:
<http://10times.com/>
```{r}
  # http://www.r-bloggers.com/mapping-biomes/
  # http://fwtools.maptools.org/

  #http://www.r-bloggers.com/no-surprises-more-people-tweet-more-visualizing-twitter-counts-during-election-day/
```


[Inspire Conference](http://inspire.ec.europa.eu/events/conferences/inspire_2014/page/home)

## Interesting geolinks

<http://www.gis-mannheim.de/>


## Writing own packages

<http://r-pkgs.had.co.nz/description.html>

## Comics

<http://xkcd.com/1138/>



## Julia Language

<http://julialang.org/learning/>

<http://www.inwt-statistics.de/blog-artikel-lesen/Statistik-Software_R.html>

<https://github.com/openlayers/openlayers>

## Further Languages

Comparison of R and other statistical programs

<http://blog.datacamp.com/statistical-language-wars-the-infograph/>

<http://www.rzbt.haw-hamburg.de/dankert/ccppjava.html/>

## Python

<http://civilstat.com/2012/10/javascript-and-d3-for-r-users-part-2-running-off-the-r-server-instead-of-python/>

<http://rforwork.info/2015/05/28/an-r-enthusiast-goes-pythonic/>

<http://www.r-bloggers.com/choosing-r-or-python-for-data-analysis-an-infographic/>

## Java

<http://clojure.org/>


## Google programming language GO

<https://golang.org/>


##  getting to know html

<https://developer.mozilla.org/en-US/docs/Web/Guide/HTML/Introduction>

## Javascript

<http://www.dateiendung.com/format/js>


## R and Javascript

<http://www.r-bloggers.com/statistical-computation-in-javascript-am-i-nuts/>

<http://www.htmlwidgets.org/>

## Running javascript using V8


```{r,eval=F}
# library(V8)
# data(diamonds, package="ggplot2")
# ct <- new_context()
# ct$assign("diamonds", diamonds)
# 
# # Load CrossFilter JavaScript library
# ct$source("http://cdnjs.cloudflare.com/ajax/libs/crossfilter/1.3.11/crossfilter.min.js")
# 
# ct$console()
```


## openlayers

<http://openlayers.org/en/v3.2.0/doc/tutorials/introduction.html>

## Some helpers

<http://www.w3schools.com/html/html_intro.asp>

## Open CPU

<https://www.opencpu.org/>


## R and Hadoop

<https://github.com/RevolutionAnalytics/RHadoop/wiki>

```{r}
# http://rapache.net/
```

## Using a database and R

<http://www.r-bloggers.com/using-azure-as-an-r-datasource-part-2-pulling-data-from-mysqlmariadb/>

## Links

<http://www.r-bloggers.com/become-an-effective-data-hacker-with-the-r-hadoop-stack/>
<http://blog.revolutionanalytics.com/2011/09/mapreduce-hadoop-r.html>


OpenGov

<http://ropengov.github.io/projects/>

## New Developments UseR 2015 in Aalborg

[Overview in German](http://blog.eoda.de/2015/07/01/eoda-auf-der-user-conference-2015-in-aalborg-die-eindruecke-vom-tutorial-tuesday/)

[Another overview](http://blog.revolutionanalytics.com/user-groups/)

Have a look at Docker
<https://www.docker.com/>

[network analysis with igraph](http://igraph.org/r/)

[Tutorial RHadoop](http://hortonworks.com/hadoop-tutorial/using-rhadoop-to-predict-visitors-amount/)

<http://www.rdatamining.com/big-data/r-hadoop-setup-guide>

[Analyze and manage Facebook ads from R](https://github.com/cardcorp/fbRads)


Get into contact
<https://ropensci.org/community/#join-us>
<https://www.r-consortium.org/>

[An alternative for rstudio](http://www.openanalytics.eu/downloads/architect)

## Further links

<http://www.r-bloggers.com/introducing-v8-an-embedded-javascript-engine-for-r/>

<http://jsfiddle.net/user/opencpu/fiddles/>

<https://www.opencpu.org/posts/v8-release-0-2/>
<https://www.r-bloggers.com/introducing-v8-an-embedded-javascript-engine-for-r/>

<http://rforge.net/JRI/index.html>


```{r,eval=F}
system.file("jri",package="rJava")
```

```{r}
# install.packages("DiscreteRV")
```

