---
title: "Some Helpers"
author: "Jan-Philipp Kolb"
date: "17. April 2015"
output: html_document
---

## HTML and CSS

<http://www.codecademy.com/tracks/web>

<http://www.w3schools.com/css/css_howto.asp>

Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css
        
        
You can enable figure captions by `fig_caption: yes` in YAML:        
        
    output:
      rmarkdown::html_vignette:
        fig_caption: yes        
        
<http://shiny.rstudio.com/articles/css.html>

        
## <http://github.org>

<http://www.molecularecologist.com/2013/11/using-github-with-r-and-rstudio/>

## rmarkdown

see the documentation for the rmarkdown package

```{r,eval=F}
library(rmarkdown)
```


Here you can find the chunk options:

<http://yihui.name/knitr/options/>


## Cite a r-package

```{r,cache=T}
citation(package = "cluster")
citation(package = "xlsx")
citation(package = "foreign")
citation(package = "mice")
```

<http://www.blopig.com/blog/2013/07/citing-r-packages-in-your-thesispaperassignments/>
