---
title: "Some Helpers"
author: "Jan-Philipp Kolb"
date: "17. April 2015"
output: html_document
---

## HTML and CSS

<http://www.codecademy.com/tracks/web>

<http://www.w3schools.com/css/css_howto.asp>

Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css
        
        
You can enable figure captions by `fig_caption: yes` in YAML:        
        
    output:
      rmarkdown::html_vignette:
        fig_caption: yes        
        
<http://shiny.rstudio.com/articles/css.html>

        
## <http://github.org>

<http://www.molecularecologist.com/2013/11/using-github-with-r-and-rstudio/>

## rmarkdown

see the documentation for the rmarkdown package

```{r,eval=F}
library(rmarkdown)
```


Here you can find the chunk options:

<http://yihui.name/knitr/options/>

[More about knittr](http://yihui.name/knitr/demo/showcase/)

Here is how to embed formulas:

<http://www.unexpected-vortices.com/sw/rippledoc/quick-markdown-example.html>


If you need a bibliography:
 <http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html>


If you want to write a vignette:
<http://www.magesblog.com/2012/01/feedback-from-vignette-survey.html>

## Cite a r-package

```{r,cache=T}
citation(package = "cluster")
citation(package = "xlsx")
citation(package = "foreign")
citation(package = "mice")
```

<http://www.blopig.com/blog/2013/07/citing-r-packages-in-your-thesispaperassignments/>

## Rstudio and git

[Rstudio and git](http://www.r-bloggers.com/rstudio-and-github/)

[Github](https://github.com/jennybc/2015-06-28_r-summit-talk/blob/master/2015-06-28_bryan-r-summit-talk.pdf)

[Github 2](http://www.r-bloggers.com/get-by-with-a-little-r-help-from-your-friends-at-github/)

[education and github](http://blog.revolutionanalytics.com/2015/06/get-your-r-education-going-with-github.html)

## What's new on R

<http://cran.r-project.org/src/base/NEWS>

[Teaching with R](http://gastonsanchez.com/teaching/)
