---
title: "The R-Journal"
author: "Jan-Philipp Kolb"
date: "12 Januar 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The R-journal

- [The archive of the R-journal](https://journal.r-project.org/archive/)


## Interesting articles in the R-journal

- Manuel J. A. Eugster and Thomas Schlesinger - [osmar: OpenStreetMap and R](https://journal.r-project.org/archive/2013-1/eugster-schlesinger.pdf)


- Patrick E. Brown [Maps, Coordinate Reference Systems and
Visualising Geographic Data with mapmisc](https://journal.r-project.org/archive/2016-1/brown.pdf)

```{r mapmisc,eval=F}
install.packages("mapmisc")
```

```{r}
library(mapmisc)
citation("mapmisc")
```

- David Kahle and Hadley Wickham - [ggmap: Spatial Visualization with
ggplot2](https://journal.r-project.org/archive/2013-1/kahle-wickham.pdf)


- Andy South - [rworldmap: A New R package for
Mapping Global Data](https://journal.r-project.org/archive/2011-1/RJournal_2011-1_South.pdf)

```{r,eval=F}
install.packages("rworldmap")
```

- Nils B. Weidmann and Kristian Skrede Gleditsch - [Mapping and Measuring Country Shapes](https://journal.r-project.org/archive/2010-1/RJournal_2010-1_Weidmann+Skrede~Gleditsch.pdf)

```{r,eval=F}
install.packages("cshapes")
```


- Stefan Wilhelm and Miguel Godinho de Matos - [Estimating Spatial Probit Models in R](https://journal.r-project.org/archive/2013-1/wilhelm-matos.pdf)


- Benedikt Gräler, Edzer Pebesma and Gerard Heuvelink - [Spatio-Temporal Interpolation using gstat](https://journal.r-project.org/archive/2016-1/na-pebesma-heuvelink.pdf)

- John Hughes - [ngspatial: A Package for Fitting the
Centered Autologistic and Sparse Spatial
Generalized Linear Mixed Models for
Areal Data](https://journal.r-project.org/archive/2014-2/hughes.pdf)

- Luca Sartore - [spMC: Modelling Spatial Random Fields
with Continuous Lag Markov Chains](https://journal.r-project.org/archive/2013-2/sartore.pdf)

## Misc

-  Paul Murrell - [The gridGraphics Package](https://journal.r-project.org/archive/2015-1/murrell.pdf)

```{r,eval=F}
install.packages("gridGraphics")
```
